`make.modifiers`

### 2023-02-21 inst/gitbook/03_make.modifiers.Rmd
added modifiers and make.modifiers examples

In the examples above, we have seen how to specify modifications to the birth death process (via `branch.length`, `selection` and `speciation`), however, one might note that these modifications are not dynamic.
In other words, throughout the process, the modifications remain constant (even if they are conditional).
It is however possible to code the `"modifiers"` so that they can be affected by `"events"` objects (see next chapter).

@@

@@

## Demo runnable

```{r, fig.height = 16, fig.width = 8, eval = FALSE}

```

>>>>

In the examples above, we have seen how to specify modifications to the birth death process (via `branch.length`, `selection` and `speciation`), however, one might note that these modifications are not dynamic.
In other words, throughout the process, the modifications remain constant (even if they are conditional).
It is however possible to code the `"modifiers"` so that they can be affected by `"events"` objects (see next chapter [on `events`](#makeevents)).

@@

```{r}
    always.false <- function() return(FALSE)
    always.one <- function(x = NULL) return(1)

    test <- make.modifiers(branch.length = branch.length.trait,
                           speciation    = speciation.trait,
                           condition     = always.false, 
                           modify        = always.one)
```

@@
